NFC and burnout in teachers - A replication and extension study

### 2022-07-20 Manuscript/Manuscript.Rmd
Update Manuscript.Rmd

abstract: |
  Burnout has become more prevalent, mainly in social jobs, but little is known about the personality traits that promote or protect against burnout.
  One of these traits is Need for Cognition (NFC), the stable intrinsic motivation to seek out and enjoy effortful cognitive activities.
  We analyzed data of N = 180 teachers to replicate results by Grass et al. (2018), who reported a mediation of NFC and the burnout subscale reduced personal efficacy by habitual reappraisal, but not by habitual suppression or self-control.
  With our data, self-control became a significant mediator when taking teaching experience into account, but neither reappraisal nor suppression did.
  We also investigated whether NFC and burnout were associated via different ratios of demands and resources, and included other variables in an exploratory approach.
  The results indicated that teachers with higher NFC and self-control have lower burnout because they experience their resources as fitting to the demands.

>>>>

abstract: |
  Burnout has become more prevalent, mainly in social jobs. While there is evidence that certain personality traits promote or protect against burnout, the role of dispositional cognitive motivation has been investigated only recently.
  One of these traits is Need for Cognition (NFC), the stable intrinsic motivation to seek out and enjoy effortful cognitive activities.
  We analyzed data of N = 180 teachers to replicate results by Grass et al. (2018), who reported a mediation of NFC and the burnout subscale reduced personal efficacy by habitual reappraisal, but not by habitual suppression or self-control.
  With our data, self-control became a significant mediator when taking teaching experience into account, but neither reappraisal nor suppression did.
  We also investigated whether NFC and burnout were associated via different ratios of demands and resources, and included other variables in an exploratory approach.
  The results indicated that teachers with higher NFC and self-control have lower burnout because they experience their resources as fitting to the demands.
